The Name of the Title is Hope

### 2023-12-13 input/7_discussion.tex
revision

\section{Discussion}
With this paper, we contributed a new way to design augmented experiences with the potential to maintain a user's SoA: a bleeding edge BCI to control EMS at moments of users' intention to interact. By leveraging an average of 11.5 EEG channels and using a simple, fast-to-compute feature, the BCI achieved a mean F1 score of .7. We demonstrated in eight participants that one effect of SoA, intentional binding, is maintained when using our system. However, the subjectively rated level of control was lower when using the system as compared to voluntary interaction without EMS. This was differentiated by participants' qualitative reports: when the stimulation aligned with participants' intentions, positive sentiments outweighed negative ones. When it did not, participants reported a negatively perceived loss of control.

% Sandwich: 
% Good -> [short] cool system, first of its kind setting out to augment user's action preceeding their movement in time
Our system was built using off-the-shelf, affordable, equipment to physically augment users' actions. Taken together, all the tech to control the users' movements, i.e., the EMS stimulation device, Arduino, and switchboard, cost less than 100 [anonymized]. While we used a 64-channel research-grade EEG system, the channel selection procedure resulted in the system ultimately using a low-density coverage of about 12 channels on average for classification. Today, many low-density EEG devices are available on consumer markets at affordable price points, see~\citet{Niso2023-ce} for a recent summary of available wireless systems.

Still, the system achieved what is considered to be a `good' F1 score of .7, and hence sometimes detected users' intention to interact. In our user study, this system performance affected users' performance in the time estimation task when comparing the three experimental conditions. We conclude that taking users' sentiments and ratings of control into account, this indicates a general modulation of agency with respect to intention-based augmentation. We believe this to be a very promising finding considering the fact that our prototype with low technological requirements still produces behavioral results indicating that intention can be detected and planned movements be augmented.

In line with the literature, we found that participants estimated the delay between tap and tone to be lower in both conditions where they were instructed to act on their own volition as compared to the passive condition~\cite{Moore2012-dk}. More recent literature has questioned the validity of the intentional binding phenomenon as a correlate of agency, stating that the effect may ``merely represent a strong case of multisensory causal binding.''~\cite{Suzuki2019-pi, Gutzeit2023-ei, Hoerl2020-my}. However, in our study, we observed the effect of compressing the action-outcome delay to be maintained even when using the system. Hence, the effect was maintained for both conditions of voluntary action.

% Bad -> (1) situate the findings of the IB, (2) bad classification metrics not good enough to feel in control
\subsection{Limitations}
Two main procedural issues arose with respect to the time estimation task: First, contrasting AUGMENTED with INTENTION, we noted that when EMS moved participants' fingers, they sometimes reported that their finger was pressing on the touchscreen for a longer duration as compared to their `normal' touchscreen tap. This may have introduced additional variance in the time estimation task since the exact moment of the tap that causes the tone is more obscure. Second, following pilot recordings, we chose to obtain participants' time estimates by asking them to type in their estimates on the keyboard. However, we observed that many participants, while perceiving a continuous distribution of the delays, did not answer at a continuous ms resolution but rather at steps of 50 or 100 ms, skewing the distribution of their answers. While many different versions of the intentional binding paradigm exist~\cite{Moore2012-dk}, we would now choose a continuous slider, perhaps set at different initial positions between trials, to obtain participants' estimates.

\subsubsection{Improving the Prediction of the Intent to (Inter-) act}
While an F1 score of .7 may be considered `good' for many classification scenarios, when aiming to elicit a feeling of control this level of performance may likely not be good enough, see~\citet{Papenmeier2022-oi} for a review. Balancing false positive rate (FPR) and true positive rate (TPR) appropriately may prove crucial in order to elicit an experience of agency.

@@

% \subsubsection{Opportunities}
\begin{comment}
% Kasahara work, Tajima, neuromodulation? reference my affordance position paper -> copy text from there!! or during painting -> scott/gehrke -> reuse image?, affordance ++ as well, 
- relevance of research for prostheses ( see https://link.springer.com/chapter/10.1007/978-3-030-38740-2_8)
% At this point in time, the movement plan is already in place and so <[rework] there is slack in the perceptual system that can be exploited so user's action can be altered with them noticing>. 
- EMS augmented interaction might make sense for bigger movements (e,g. back muscle to support lifting) -> might have less effect (negative) effect on the feeling of control, since it is a less specific movement
- However, brain signal might not be the best indicator in such cases (simply motion tracking indicating the start of the movement)

% playful experiences: EMS

\missingfigure[]{Hand weg zieh spiel foto, beispielhafte playful experience in der es interessant ist mit dem agency konzept herumzuspielen und es spielerisch zu entdecken?}

- a bit on HCINT?
% What do I want to say here? Just in general describe the level of integrations that exist and then say where we would place our prototype? Or is this more interesting for a later discussion part? Maybe yes, just move this to a later stage, it does not really add here and better fits in the discussion, also then to discuss the results and what it means to be integrated in a certain way

%- not only physical integration but also other adpative interfaces, or control of mobile phone (see Cornelio2022 review); % say here somewhere what action augmentation is and how it differs from body and environment/outcome augmentation

% briefly summarize the papers on discriminating action augementation and other such things, reference cornelio 2022 paper
% Previous research on augmented technology and ideas to maintain sense of of agency
% The experience of being integrated with a technology, or of being one ``human-technology assemblage'' <REF where is this from, Danry2022 used it>

% Action augmentation technology using motor actuation aims to augment the user’s actions diminishing the SoA (see Cornelio 2022). 
% - add research
% Here I want to say where our system lies within the design space of augmentation devices and <cornelio2022> gives a good nomenclature for this. Then transition over to how agency is important to consider when localizing our prototpye and then in the next paragraph talk about what agency from a neuroscientific perspective
\end{comment}

@@

With AI technologies becoming more and more ubiquitous in our everyday life, questions about how agency is shared between us humans and these AI technologies arise on a regular basis. With the likely future that these systems move directly onto our bodies, alignment with users' intentions will be the \textit{key} component driving their adoption.

>>>>

\section{Discussion}
With this paper, we contributed a new way to design the experience of action augmentation augmented experiences with the potential to maintain a user's SoA: a BCI to control EMS at moments of users' intention to interact. By leveraging an average of 11.5 EEG channels and using a simple, fast-to-compute feature, the BCI achieved a mean F1 score of .7. We demonstrated in eight participants that one effect of SoA, intentional binding, is maintained when using our system. However, the subjectively rated level of control was lower when using the system as compared to voluntary interaction without EMS. This was differentiated by participants' qualitative reports: when the stimulation aligned with participants' intentions, positive sentiments outweighed negative ones. When it did not, participants reported a negatively perceived loss of control.

Our system was built using off-the-shelf, affordable, equipment to physically augment users' actions. Taken together, all technical devices to control the users' movements, i.e., the EMS stimulation device, Arduino, and switchboard, cost less than 100 Euros. While we used a 64-channel research-grade EEG system, the channel selection procedure resulted in the system ultimately using a low-density coverage of about 12 channels on average for classification. Today, many low-density EEG devices are available on consumer markets at affordable price points, see~\citet{Niso2023-ce} for a recent summary of available wireless systems.

Still, the system achieved what is considered to be a `good' F1 score of .7, and hence sometimes detected users' intention to interact. In our user study, this system performance affected users' tendency for temporal binding when comparing the three experimental conditions. We conclude that taking users' sentiments and ratings of control into account, this indicates a general modulation of agency for our intention-based augmentation. We believe this to be a very promising finding because our prototype with low technological requirements still produces behavioral results indicating that intention can be detected and planned movements be augmented.

Our system ran at a 10 Hz update rate. This was chosen in order to avoid buffer overflow due to the fact that the end-to-end computing latency from measuring the physiological signal to outputting the predicted class and probability took about 40 ms. The RP is reported to occur several hundred milliseconds prior to the physical movement~\cite{Schurger2021-vp}. Therefore, our augmentation should have resulted in a motion preemption, considering subtracting the computing latency and a delay that the EMS stimulation takes to affect the muscle from the RP-based intention detection. However, it is difficult to assess whether participants' movements were in fact pre-empted as no label exists for the `true' intention onset to compare the classifier to. That participants were able to act on their own volition, and hence no labelling of their movement intention could be derived, is the key distinction to related works using controlled stimulus-response paradigms.

However, we learned from these paradigms that increasing participants' reaction times by about 80 ms is optimal with regards to maintaining SoA~\cite{Kasahara2019-sk}. On one hand, our system is capable of delivering pre-emption within this `SoA-optimal' time range. On the other hand, however, the performance of the sub-optimal performance of the classifier means a lot of variation due to false positive detections. While in some cases, as we observed in the users' comments, the stimulation may have pre-empted a user's motion, false positive stimulation may have had a significant impact on the overall impression of the system, see section~\ref{improving_classifier} below.

In line with the literature, we found that participants estimated the delay between tap and tone to be lower in both conditions where they were instructed to act on their own volition as compared to the passive condition~\cite{Moore2012-dk}. We point out that recent literature has questioned the validity of the intentional binding phenomenon as a correlate of agency, stating that the effect may ``merely represent a strong case of multisensory causal binding.''~\cite{Suzuki2019-pi, Gutzeit2023-ei, Hoerl2020-my}. However, in our study, we observed the effect of compressing the action-outcome delay to be maintained even when using the system. Hence, the effect was maintained for both conditions of voluntary action.

% Bad -> (1) situate the findings of the IB, (2) bad classification metrics not good enough to feel in control
\subsection{Limitations}
Two main procedural issues arose concerning the time estimation task: First, contrasting AUGMENTED with INTENTION, we noted that when EMS moved participants' fingers, they sometimes reported that their finger was pressing on the touchscreen for a longer duration as compared to their `normal' touchscreen tap. This may have introduced additional variance in the time estimation task since the exact moment of the tap that causes the tone is more obscure. Second, following pilot recordings, we chose to obtain participants' time estimates by asking them to type in their estimates on the keyboard. However, we observed that many participants, while perceiving a continuous distribution of the delays, did not answer at a continuous ms resolution but rather at steps of 50 or 100 ms, skewing the distribution of their answers. While many different versions of the intentional binding paradigm exist~\cite{Moore2012-dk}, we would choose a continuous slider for future experiments with different initial positions over trials to reduce the bias in participants' estimates.

\subsubsection{Improving the Prediction of the Intent to (Inter-) act}\label{improving_classifier}
While an F1 score of .7 may be considered `good' for many classification scenarios, when aiming to elicit a feeling of control this level of performance may likely not be good enough, see~\citet{Papenmeier2022-oi} for a review. Balancing false positive rate (FPR) and true positive rate (TPR) appropriately may prove crucial to elicit an experience of agency.

@@

@@

With AI technologies becoming more and more ubiquitous in our everyday lives, questions about how agency is shared between us humans and AI technologies arise regularly. With the likely future that these systems move directly onto our bodies, alignment with users' intentions will be the \textit{key} component driving their adoption.
